Effects of the body force on the evacuation dynamics

### 2019-12-27 paper.tex
Update paper.tex

\begin{equation}
 \mathbf{f}_s^{(i)}=A\,e^{(R_{ij}-r_{ij})/B}\hat{\mathbf{n}}_{ij}
 \label{eqn_social}
\end{equation}

@@

\begin{equation}
 \mathbf{f}_g^{(ij)}=\kappa\,(R_{ij}-r_{ij})\,\Theta(R_{ij}-r_{ij})
\,(\Delta\mathbf{v}^{(ij)}\cdot\hat{\mathbf{t}}_{ij})\,\hat{\mathbf{t}}_{ij}+
k\,(R_{ij}-r_{ij})\,\Theta(R_{ij}\,\hat{\mathbf{n}}_{ij}
-r_{ij})\label{eqn_friction}
\end{equation}

\noindent where $\Theta(R_{ij}-r_{ij})$ equals unity if $R_{ij}>r_{ij}$ and 
vanished otherwise. $\Delta\mathbf{v}^{(ij)}\cdot\hat{\mathbf{t}}_{ij}$ 
represents the difference between the tangential velocities of the sliding 
bodies (or between the individual and the walls).    \\

>>>>

\begin{equation}
 \mathbf{f}_s^{(i)}=A\,e^{(R_{ij}-r_{ij})/B}\,\hat{\mathbf{n}}_{ij}
 \label{eqn_social}
\end{equation}

@@

\begin{equation}
 \mathbf{f}_g^{(ij)}=\kappa\,g(R_{ij}-r_{ij})\,
(\Delta\mathbf{v}^{(ij)}\cdot\hat{\mathbf{t}}_{ij})\,\hat{\mathbf{t}}_{ij}+
k\,g(R_{ij}-r_{ij})\,
\,\hat{\mathbf{n}}_{ij}\label{eqn_friction}
\end{equation}

\noindent where $g(R_{ij}-r_{ij})$. $\Theta(R_{ij}-r_{ij})$ equals R_{ij}-r_{ij} 
if $R_{ij}>r_{ij}$ and vanished otherwise. 
$\Delta\mathbf{v}^{(ij)}\cdot\hat{\mathbf{t}}_{ij}$ represents the difference 
between the tangential velocities of the sliding bodies (or between the 
individual and the walls).    \\
